---
title: "SSPPI Strengths"
author: Rémi Daigle, Jaimie Harbin, Catalina Gomez
format: 
  html: 
    code-fold: true
    code-tools: true
    toc: true
    toc_float: true
    embed-resources: true
---



```{r loading packages,warning=FALSE,message=FALSE}
require(tidyverse)
require(ggwordcloud)
require(ggraph)
require(igraph)
require(grid)
require(gridExtra)
require(cowplot)
```
 First we read in the data from the [team survey](https://forms.office.com/r/aq4SMKM83a), the team was asked to share their top 5 CliftonStrengths after the group exercise(s). For more information about this team exercise, please visit the [Inner Strengths Exercise](https://086gc.sharepoint.com/sites/SciencePlanningAdviceandDataSPAD/SitePages/Inner-Strengths-Exercise.aspx)
 
```{r reading data and wrangling}
domains <- read.csv("domains.csv")

strengths <- readxl::read_xlsx("Our Super Powers (1-15).xlsx",
                               skip=1,
                               col_names = c("ID",
                                             "Start_time",
                                             "Completion_time",
                                             "Email",
                                             "Name",
                                             "Last_modified_time",
                                             "Top_5_strengths")) %>% 
  tidyr::separate_longer_delim(Top_5_strengths,delim=";") %>%
  mutate(Top_5_strengths=replace(Top_5_strengths,Top_5_strengths=="Responsability",c("Responsibility"))) %>% 
  mutate(Top_5_strengths=replace(Top_5_strengths,Top_5_strengths=="Self-assurance",c("Self-Assurance"))) %>%
  filter(Top_5_strengths!="",ID!=7) %>% 
  left_join(domains,by=c("Top_5_strengths"="Strength"))

counts <- strengths %>% 
  group_by(Top_5_strengths,Domain) %>% 
  reframe(n=n())
```

# Frequency and Evenness

Now let's look at how frequently each strength was identified our team. Below is a frequency plot for the whole team and the colours indicate the strength's domain.

```{r evenness plot}
colors <- c("Executing"="#2c7bb6",
            "Influencing"="#abd9e9",
            "Relationship Building"="#fdae61",
            "Strategic Thinking"="#d7191c")

p <- ggplot(counts %>% 
              select(-Domain) %>% 
              full_join(domains,by=c("Top_5_strengths"="Strength")) %>% 
              mutate(n=if_else(is.na(n),0,n),
                     Top_5_strengths=factor(Top_5_strengths,levels=domains$Strength,ordered=TRUE))
              )+
  geom_col(aes(x=Top_5_strengths,y=n,fill=Domain),color="transparent")+
  # scale_fill_brewer(palette="RdYlBu",type="qual",direction=-1)
  scale_fill_manual(values=colors)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
p
```


Below is the same information, but as a word cloud with size being scaled to frequency (yes, I begrudgingly had to plot the legend separately for now):

```{r wordcloud}

ggplot(counts)+
  geom_text_wordcloud(aes(label=Top_5_strengths,size=n,color=Domain))+
  scale_size_area(max_size = 15) +
  # scale_color_brewer(palette="RdYlBu",type="qual",direction=-1)+
  scale_color_manual(values=colors)+
  theme_minimal()

l <- get_legend(p)
grid.newpage()
grid.draw(l)
```

# Similarity Networks

To see the similarity between team members in terms of matching strengths, I created a network graph that shows the number of matching strengths between team members as the thickness of the lines.

```{r simple graph}
nodes <- unique(strengths$Name)
edgelist <- data.frame()
for(i in nodes){
  for(j in nodes){
    if(i!=j&!any(edgelist$id1==j&edgelist$id2==i)){
      s1 <- strengths$Top_5_strengths[strengths$Name==i]
      s2 <- strengths$Top_5_strengths[strengths$Name==j]
      if(any(s1 %in% s2)){
      edgelist <- rbind(edgelist,
                        data.frame(
                          id1=i,
                          id2=j,
                          similarity=as.integer(sum(s1 %in% s2)
                        )))
      }
      
      
    }
  
}
}


```

```{r simple graph plot, message=FALSE, warning=FALSE}
g <- graph_from_data_frame(filter(edgelist,similarity>0), directed = FALSE, nodes) 
ggraph(g,weight=similarity)+
  geom_edge_diagonal(aes(width=similarity),alpha=0.5)+
  geom_node_point(size=3,colour="yellow")+ 
  # geom_node_text(aes(label = name), repel=TRUE)+
  theme(panel.background = element_blank())+
  theme(legend.key=element_blank())
```

Going a bit deeper, I separated each strength as a separate labeled (for each strength) and color coded (for domains) line.

```{r multi-edge graph and plot,fig.fullwidth=TRUE,fig.width=11,message=FALSE}
nodes <- unique(strengths$Name)

  

strengthlabels <- strengths %>%
  group_by(Name) %>% 
  summarize(strength=paste(Top_5_strengths,collapse="\n "))

edgelist <- data.frame()
for(i in nodes){
  for(j in nodes){
    if(!any(edgelist$id1==j&edgelist$id2==i)){
      s1 <- strengths$Top_5_strengths[strengths$Name==i]
      s2 <- strengths$Top_5_strengths[strengths$Name==j]
      if(any(s1 %in% s2)){
        edgelist <- rbind(edgelist,
                          data.frame(
                            id1=i,
                            id2=j,
                            strength=s1[s1 %in% s2] 
                          )
        )
      }
    }
  }
}

test <- edgelist %>% 
  left_join(domains,by=c("strength"="Strength")) %>% 
  left_join(strengthlabels,by=c("id1"="Name")) %>% 
  select(-id1) %>% 
  rename(id1=strength.y,strength=strength.x) %>% 
  left_join(strengthlabels,by=c("id2"="Name")) %>% 
  select(-id2) %>% 
  rename(id2=strength.y,strength=strength.x) %>% 
  select(id1,id2,strength,Domain)
  # mutate(id1=left_join(as.data.frame(id1),strengthlabels,by=c("id1"="Name")) %>% select(strength),
  #        id2=left_join(as.data.frame(id2),strengthlabels,by=c("id2"="Name")) %>% select(strength))

g <- graph_from_data_frame(test, directed = FALSE) 
ggraph(g)+
  geom_edge_fan(aes(color=Domain,label=strength),
                label_alpha = 0.75,
                label_colour = "grey",
                angle_calc = "along")+
  scale_edge_color_manual(values=colors)+
  geom_node_point(size=3)+
  geom_node_text(aes(label = name), repel=TRUE)+
  theme(panel.background = element_blank())+
  theme(legend.key=element_blank())

```
